Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-11-16 prop_letter.tex
Updating what Prof. Ortiz typed...

The question of how to address this controversy, and the effect of 
finite precision on measurements in general, is therefore 
a fundamental problem.  How does one
develop mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement?   In this paper, we extend our previous work on the
foundations of computability in quantum physics by exploring the
application of interval-valued probability measures (IVPMs) to
achieving a coherent formulation of finite-resource quantum mechanics.
From this starting point, we develop a mathematical framework that includes the
uncertainties of finite precision and imperfections in the quantum
measurement process.  In particular, we are able to suggest a way to quantify
the concept of imperfect quantum measurement and its impact on the interpretation of
the Kochen-Specker and Gleason theorems and their implications for the
foundations of quantum mechanics.  We have reason to believe that
essential objectives of our program to achieve a computable theory of
quantum mechanics and finite-resource measurement, attempted
previously with computable number
systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical IVPMs~\cite{JamisonLodwick2004} to the quantum
domain.  We thus begin by axiomatizing a quantum interval-valued
probability measure (QIVPM) framework.

@@

The paper is organized as follows.  In Sec.~\ref{sec:fuzzy} we begin
by introducing the foundations of quantum probability space and fuzzy
measurement.  We then move on to introduce the concept of quantum
interval valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
The QIVPMs will provide the mathematical framework we need to quantify
the impact of finite precision measurements on quantum mechanics.  For
instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
validity of a contextual measurement, thus addressing the conditions
under which the Kochen-Specker theorem applies.  This provides a way
of not only resolving the Meyer-Mermin debate, but also revealing of a
precise transition to non-contextuality; these are the results of our
Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
study Gleason's theorem in the context of imprecise measurements,
concluding that QIVPMs provide a framework with quantitative bounds in
which Gleason's theorem, while formally invalid in a universe with
bounded resources, holds asymptotically in a mathematically precise
way.  Finally, we present our conclusions in
Sec.~\ref{sec:Conclusion}.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950bibTeX,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$ satisfying the condition $P^2=P$. These include the
empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
quantum state (an element of a Hilbert space), sums of
\emph{orthogonal} projectors $P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
$P_0P_1=P_1P_0$. In a quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
the set of all projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space ${\cal H}$ of dimension $d$ and a probability assignment
for every projector $P$, we can define the expectation value of an
observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in \mathbb{R}$, as:
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{d}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
\end{equation}

@@

The above axioms describe a mathematical idealization involving
infinitely precise measurements. In an actual experimental setup with
an ensemble of quantum states that are not exactly identically
prepared, and with small imperfections and inaccuracies in measuring
devices, an experimenter might only be able to determine that the
probability of an event $P$ is concentrated in the range $[0.49,0.51]$
instead of being precisely $0.5$. The spread in this range depends on
the quantities of resources (time, energy, money, etc.) that are
devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

In the remainder of this section, we will show that our definition of
QIVPMs is consistent with classical IVPMs in the sense that a
restriction of QIVPMs to commuting events recovers the definition of
classical IVPMs. To formalize this connection between QIVPMs and
classical IVPMs, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is consistent with a state $\rho$ and projector~$P$ if the interval
$\bar{\mu}(P)$ contains the exact probability calculated by the Born
rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

For example, a well-defined  
QIVPM, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, is:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise.}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question; any quantum
state would be consistent with $\bar{\mu}_{1}$ on any projectors. That
is, $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is the set of all
states. The subspace
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\label{eq:classical-no-information-IVPM}
\end{equation}
that corresponds to a classical IVPM. Indeed, if we identify the
states~$\proj{0}$ and $\proj{1}$ with the head and the tail of a coin,
respectively, then $\bar{\mu}_{2}$ represents the situation in which
an experimenter knows nothing about a coin before she tosses
it. Moreover, for each $p\in\left[0,1\right]$, the
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
with probability~$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
should be consistent with the situation for which an experimenter has
no prior knowledge.

@@

The expectation value of an observable $\mathbf{O}$ in a Hilbert space
of dimension $d$ relative to a 0-deterministic QIVPM is fully
determinate and is equal to one of the eigenvalues $\lambda_i$ of that
observable. To see this, note that given an orthonormal basis
$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
0-deterministic QIVPM must map exactly one of the projectors
$\proj{\psi_i}$ to $\necess$ and all others to $\imposs$. This is
because, by Eq.~(\ref{eq:necess}), we have
$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
others mapped to $\imposs$. Given any state~$\rho$ that is consistent
with this QIVPM on all the projectors in $\Omega$, we have by
Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map
exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
an observable has a spectral decomposition along $\Omega$ then, by
Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
$\muB_{\rho}$ is the eigenvalue $\lambda$ whose projector
is mapped to 1. It therefore follows, by
Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
value relative to the 0-deterministic~${\bar{\mu}}$ is fully
determinate and lies in the interval $[\lambda,\lambda]$.

@@

The proof is by contradiction: Suppose there is a
$\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We will use this
assumed QIVPM to construct the following 0-deterministic QIVPM
$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
  \imposs,\necess\right\}$:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\]
However, since we know that 0-deterministic QIVPMs do not exist, the
map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
indeed a 0-deterministic QIVPM by checking that for orthogonal
operators~$P_{0}$ and $P_{1}$, we have that
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
when
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or
$\left[1-\delta,1\right]$ and the latter is excluded, then
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
theorem holds when $\delta<\frac{1}{3}$.

@@

We have quantified one aspect of uncertainty in quantum
mechanics---due to the imprecise nature of devices---which is a novel
addition to the theory of measurement. Indeed, as Heisenberg
emphasized in his famous microscope
example~\cite{Heisenberg1983apsrev4}, the conventional theory
of measurement states that it is impossible to precisely measure any
property of a system without disturbing it somewhat. There are
fundamental limits to what one can measure and these limits are
typically attributed to complementarity. Our imprecision is an
\emph{additional} indeterminacy to the inherent probabilistic nature
of quantum mechanics.

@@

As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. Indeed, in
the limit, the intervals become \imposs, \necess, and \unknown and
every state is consistent with an assignment that states that its
projections are unknown. There is however a subtlety: as shown in the
theorem below, an arbitrary assignment of intervals to projectors
might be globally inconsistent.

>>>>

The question of how to address this controversy, and the effect of 
finite precision on measurements in general, is therefore 
a fundamental problem of physics.  How does one
develop mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement?   In this paper, we extend our previous work on the
foundations of computability in quantum physics by exploring the
application of interval-valued probability measures (IVPMs) to
achieving a coherent formulation of finite-resource quantum mechanics.
From this starting point, we develop a mathematical framework that includes the
uncertainties of finite precision and imperfections in the quantum
measurement process.  In particular, we are able to suggest a way to quantify
the concept of imperfect quantum measurement and its impact on the interpretation of
the Kochen-Specker and Gleason theorems and their implications for the
foundations of quantum mechanics.  We have reason to believe that
essential objectives of our program to achieve a computable theory of
quantum mechanics and finite-resource measurement, attempted
previously with computable number
systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be achievable by
extending classical IVPMs~\cite{JamisonLodwick2004} to the quantum
domain.  We thus begin by axiomatizing a quantum interval-valued
probability measure (QIVPM) framework.

@@

The paper is organized as follows.  In Sec.~\ref{sec:fuzzy} we begin
by introducing the foundations of quantum probability space and fuzzy
measurement.  We then move on to introduce the concept of quantum
interval-valued probability in Sec.~\ref{sec:Interval-Uncertainty}.
The QIVPMs will provide the mathematical framework we need to quantify
the impact of finite precision measurements on quantum mechanics.  For
instance, in Sec.~\ref{sec:Kochen-Specker}, we quantify the domain of
validity of a contextual measurement, thus addressing the conditions
under which the Kochen-Specker theorem applies.  This provides a way
of not only resolving the Meyer-Mermin debate, but also revealing of a
precise transition to non-contextuality; these are the results of our
Thm.~\ref{cor:Kochen-Specker-IVPM}.  In Sec.~\ref{sec:Gleason}, we
study Gleason's theorem in the context of imprecise measurements,
concluding that QIVPMs provide a framework with quantitative bounds in
which Gleason's theorem, while formally invalid in a universe with
bounded resources, holds asymptotically in a mathematically precise
way.  Finally, we present our conclusions in
Sec.~\ref{sec:Conclusion}.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950bibTeX,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$ satisfying the condition $P^2=P$. These include the
empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
quantum state (an element of a Hilbert space ${\cal H}$), sums of
\emph{orthogonal} projectors $P_0$ and~$P_1$ with $P_0P_1=\mathbb{0}$,
and products of \emph{commuting} projectors $P_0$ and~$P_1$ with
$P_0P_1=P_1P_0$. In a quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
each event~$P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$ is
the set of all events, projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space ${\cal H}$ of dimension $d$ and a probability assignment
for every projector $P$, we can define the expectation value of an
observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=1}^{d}\lambda_{i}P_{i}$, with eigenvalues $\lambda_i \in \mathbb{R}$, as:
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=1}^{d}\lambda_{i}\mu(P_{i})\,.\label{eq:quantum-expectation}
\end{equation}

@@

The above axioms describe a mathematical idealization involving
infinitely precise measurements. In an actual experimental setup with
an ensemble of quantum states that are not exactly identically
prepared, and with small imperfections and inaccuracies in measuring
devices, an experimenter might only be able to determine that the
probability of an event $P$ is concentrated in the range $[0.49,0.51]$
instead of being precisely $0.5$. The spread in this range depends on
the amount of resources (time, energy, money, etc.) that are
devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

In the remainder of this section, we will show that our definition of
QIVPMs is consistent with classical IVPMs in the sense that a
restriction of QIVPMs to mutually commuting events recovers the definition of
classical IVPMs. To formalize this connection between QIVPMs and
classical IVPMs, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is consistent with a state $\rho$ and projector~$P$ if the interval
$\bar{\mu}(P)$ contains the exact probability calculated by the Born
rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

For example, a well-defined  
QIVPM, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, is:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise.}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question; any quantum
state would be consistent with $\bar{\mu}_{1}$ on any projectors. That
is, $\coreBorn\left(\bar{\mu}_{1},\events\right)$ is the set of all
states. The subspace
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a subspace of commuting events. Restricting $\bar{\mu}_{1}$
to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a measure
$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\label{eq:classical-no-information-IVPM}
\end{equation}
that corresponds to a classical IVPM. Indeed, if we identify the
states~$\proj{0}$ and $\proj{1}$ with the head and the tail of a coin,
respectively, then $\bar{\mu}_{2}$ represents the situation in which
an experimenter knows nothing about a coin before she tosses
it. Moreover, for each $p\in\left[0,1\right]$, the
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical coin
with probability~$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent
with~$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin
should be consistent with the situation for which an experimenter has
no prior knowledge.

@@

The expectation value of an observable $\mathbf{O}$ in a Hilbert space
${\cal H}$ of dimension $d$ relative to a 0-deterministic QIVPM is fully
determinate and is equal to one of the eigenvalues $\lambda_i$ of that
observable. To see this, note that given an orthonormal basis
$\Omega=\{ \ket{\psi_0},\ket{\psi_1},\ldots,\ket{\psi_{d-1}}\}$, a
0-deterministic QIVPM must map exactly one of the projectors
$\proj{\psi_i}$ to $\necess$ and all others to $\imposs$. This is
because, by Eq.~(\ref{eq:necess}), we have
$\bar{\mu}(\Sigma_{j=0}^{d-1}{\proj{\psi_j}})=\necess$ and by inductively
applying Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
we must have one of the $\bar{\mu}(\proj{\psi_i})=\necess$ and all
others mapped to $\imposs$. Given any state~$\rho$ that is consistent
with this QIVPM on all the projectors in $\Omega$, we have by
Eq.~(\ref{eq:hbar}) that $\muB_{\rho}$ must also map
exactly one of the projectors in $\Omega$ to 1 and all others to 0. If
an observable has a spectral decomposition along $\Omega$ then, by
Eq.~(\ref{eq:quantum-expectation}), its expectation value relative to
$\muB_{\rho}$ is the eigenvalue $\lambda_i$ whose projector
is mapped to 1. It therefore follows, by
Eq.~(\ref{eq:quantum-interval-expectation-core}), that the expectation
value relative to the 0-deterministic~${\bar{\mu}}$ is fully
determinate and lies in the interval $[\lambda_i,\lambda_i]$.

@@

The proof is by contradiction: Suppose there is a
$\delta$-deterministic
QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. We will use this
assumed QIVPM to construct the following 0-deterministic QIVPM
$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
  \imposs,\necess\right\}$:
\[
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\]
However, since we know that 0-deterministic QIVPMs do not exist, the
map $\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ does
not exist. It remains to verify that $\bar{\mu}^{\textrm{D}}$ is
indeed a 0-deterministic QIVPM by checking that for orthogonal
projectors~$P_{0}$ and $P_{1}$, we have that
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$
implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$~\citep{TaiThesis2018}. Indeed
when
$\bar{\mu}^{\textrm{D}}\left(P_{0}\right)=\bar{\mu}^{\textrm{D}}\left(P_{1}\right)=\imposs$,
we have both $\bar{\mu}\left(P_{0}\right)$ and
$\bar{\mu}\left(P_{1}\right)\subseteq\left[0,\delta\right]$ which
implies
$\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,2\delta\right]$.
When $\delta<\frac{1}{3}$, i.e., $2\delta<1-\delta$, it follows that
$\bar{\mu}\left(P_{0}+P_{1}\right)$ cannot be a subset of
$\left[1-\delta,1\right]$. Since $\bar{\mu}\left(P_{0}+P_{1}\right)$
is a subset of either $\left[0,\delta\right]$ or
$\left[1-\delta,1\right]$ and the latter is excluded, then
$\bar{\mu}\left(P_{0}+P_{1}\right)$ must be a subset of
$\left[0,\delta\right]$, which implies
$\bar{\mu}^{\textrm{D}}\left(P_{0}+P_{1}\right)=\imposs$. Thus the
theorem holds when $\delta<\frac{1}{3}$.

@@

We have quantified one important aspect of uncertainty in quantum
mechanics---due to the imprecise nature of devices---which is a novel
addition to the theory of measurement. Indeed, as Heisenberg
emphasized in his famous microscope
example~\cite{Heisenberg1983apsrev4}, the conventional theory
of measurement states that it is impossible to precisely measure any
property of a system without disturbing it somewhat. Thus, there are
fundamental limits to what one can measure and these limits have traditionally 
been attributed to complementarity. Our imprecision represents an 
\emph{additional} source of indeterminacy to the inherent probabilistic nature
of quantum mechanics.

@@

As the intervals in the image of a QIVPM become less and less sharp,
we expect more and more states to be consistent with it. Indeed, in
the limit, the intervals become \imposs, \necess, and \unknown,  and
every state is consistent with an assignment that states that its
projections are unknown. There is however a subtlety: as shown in the
theorem below, an arbitrary assignment of intervals to projectors
might be globally inconsistent.
